Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-07-17 surfaces-write-up/surface-write-up.tex
delete extraneous .

\todo{Aaron: Give some definitions to make clear what the structure of divisors are}
\todo{Aaron: clarify that $R_D$ is assumed to have both positive bidegrees}
\todo{Aaron: Have $\ell_{i,j}$ been defined?}
Let $D=\sum_{i=1}^n \alpha_i D_i \in \mathbb{Q} \otimes \di(\hirz_
m).$ such
that $D_1, D_2, D_3,$ and $D_4$ are distinct divisors with bi-degrees $(1,0)
, (1,0), (0,1)$, and $(0,1)$ respectively. Let $D_i = V(f_i)$ where
$f_i \in \sco(\bida_i, \bidb_i)$.  
Then, $f_1$ and $f_2$ are independent linear
polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
linear polynomials in $y_0$ and $y_1$. \todo{Talk a little about Hirzebruch surfaces before this paragraph; especially, describe what it's sections look like.}

>>>>

\todo{Aaron: Give some definitions to make clear what the structure of divisors are}
\todo{Aaron: clarify that $R_D$ is assumed to have both positive bidegrees}
\todo{Aaron: Have $\ell_{i,j}$ been defined?}
Let $D = \sum_{i = 1}^n \alpha_i D_i \in \mathbb{Q} \otimes \di (\hirz_m)$ such
that $D_1, D_2, D_3,$ and $D_4$ are distinct divisors with bi-degrees $(1,0)
, (1,0), (0,1)$, and $(0,1)$ respectively. Let $D_i = V(f_i)$ where
$f_i \in \sco(\bida_i, \bidb_i)$.  
Then, $f_1$ and $f_2$ are independent linear
polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
linear polynomials in $y_0$ and $y_1$. \todo{Talk a little about Hirzebruch surfaces before this paragraph; especially, describe what it's sections look like.}
